Compositional Quantitative Resource Analysis of C Programs

### 2014-06-26 paper/main.tex
add some explanations in the soundness

Using this semantic validity  we can define the validity of
a function context $\Delta$ that we write $\validC n \Delta$ as
\begin{align*}
  &\forall f .\, \Delta(f) =
    \forall z \, \vec v \, v .(P_f \, z \, \vec v, Q_f \, z \, v)
    \implies \\
  &\qquad \forall z \, \vec v .\,
  \valid n \bot {Q_f \, z} {P_f \, z \, \vec v} {S_f} \bot ,
\end{align*}
where $S_f$ is the body of the function $f$.

\begin{theorem}[Soundness of the logic]
  If $\Delta; B; R \vdash \htriple P S Q$ is derivable, then
  $$
    \forall n .\, \validC n \Delta
      \implies \forall n .\, \valid n B R P S Q.
  $$
\end{theorem}

>>>>

Using this semantic validity  we can define the validity of
a function context $\Delta$ that we write $\validC n \Delta$ as
\begin{align*}
  &\forall f .\, \Delta(f) =
    \forall z \, \vec v \, v .(P_f \, z \, \vec v, Q_f \, z \, v)
    \implies \\
  &\qquad \forall z \, \vec v .\,
  \valid n \bot {Q_f \, z} {P_f \, z \, \vec v} {S_f} \bot ,
\end{align*}
where $S_f$ is the body of the function $f$.
%
\begin{theorem}[Soundness of the logic]
  If $\Delta; B; R \vdash \htriple P S Q$ is derivable, then
  $$
    \forall n .\, \validC n \Delta
      \implies \valid {n {+} 1} B R P S Q.
  $$
\end{theorem}
%
\noindent
If $S$ is a complete program and $\Delta$ is empty by
expanding the definitions and remarking that $\validC n \Delta$
and $\safeK n B R Q \Kstop$ are true for every $n$ we get that 
$$
  \forall n .\, \safe n P S \Kstop.
$$
This means that for any starting state $\state$, $P(\state)$
provides enough resource for any run of the program $S$.  This
setting is actually the main use case of the previous theorem
which is stated as a stronger result to allow a proof by
induction.
